Analysing the factors influencing the wages of the US workforce

### 2024-11-26 paper/paper.qmd
add weakness

Some important variables were not included in the analysis, such as industry classification. While industry significantly affects income, its complex structure and lack of standardized categories made it difficult to analyze. This exclusion might have introduced bias into the results. To simplify the model, smaller racial groups, such as Japanese, Indigenous, and multiracial individuals, were categorized as “Other.” Although this made the analysis manageable, it overlooked finer details in racial differences. Future studies could refine these categories and include more detailed variables when sample sizes allow.

>>>>

Some important variables were not included in the analysis, such as industry classification. While industry significantly affects income, its complex structure and lack of standardized categories made it difficult to analyze. This exclusion might have introduced bias into the results. To simplify the model, smaller racial groups, such as Indigenous, and multiracial individuals, were categorized as “Other.” Although this made the analysis manageable, it overlooked finer details in racial differences. Future studies could refine these categories and include more detailed variables when sample sizes allow.
